A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-11-29 writeup/revision 1/paper.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
\centering
\scriptsize
\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
\hline
workers & quality & speed & \\\hline
%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
%&&slow& ar ga he pa sv tr\\\cline{2-4}
%& low or medium &fast& hi mr ta ur \\\cline{3-4}
%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}   Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
& low or  &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
&medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
few &high  &fast& bs hr mk ms sh\\\cline{3-4}
&&slow&af an ast bcl be bg cs da el eu fi fy gl ht hu id ilo is ja jv kk ko lt mg nds no pam scn sk sl sq th uk uz war yo\\\cline{2-4}
&low or  &fast&--\\\cline{3-4}
&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}am az br ca cy hy ka lb lv nap nn pms ps so su sw tt vi wa \\\hline
none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}diq eo fa io ku qu wo \\\hline
\end{tabular}
\caption{The green box shows the languages which we have found most supported by MTurk in terms of worker population, worker ability, and speed of completion. Languages have ``many'' workers if we recorded more than 50 active in-region Turkers. Languages are ``high'' quality if they average greater than 70\% accuracy on our controls. Languages are ``fast'' if all of our translations (approx. 10,000 words each) were completed within two weeks.}
\label{recommendations}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
\centering
\scriptsize
\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
\hline
workers & quality & speed & \\\hline
%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
%&&slow& ar ga he pa sv tr\\\cline{2-4}
%& low or medium &fast& hi mr ta ur \\\cline{3-4}
%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}   Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
& low or  &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
&medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, Ukranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
&low or  &fast&--\\\cline{3-4}
&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
\end{tabular}
\caption{The green box shows the languages which we have found most supported by MTurk in terms of worker population, worker ability, and speed of completion. Languages have ``many'' workers if we recorded more than 50 active in-region Turkers. Languages are ``high'' quality if they average greater than 70\% accuracy on our controls. Languages are ``fast'' if all of our translations (approx. 10,000 words each) were completed within two weeks.}
\label{recommendations}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
